---
title: "Developing Data Products Final Projest"
author: "Shelby F"
date: "5/25/2022"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(shiny)
library(plotly)
data("CO2")
```

## Shiny App for Box Plots 

This Shiny App use the built in data set, CO2 and creates a box plot. The user can select the data to plot and what variable to separate it by. 

## CO2 Data

The CO2 Data Set compares 3 plants with 2 controlled variables. The first, two locations and second, two temperatures. 

Cities
- Quebec
- Mississippi 

Conditions (Treatment)
- Non chilled
- Chilled

## App Inputs

The user has a drop down menu to select CO2 Concentration or Uptake to be plotted.
They then select the variable, they can select to see all 12 plant variations, or by temperature or location. 
The app will update in real time and the labels are interactive.

## Slide with Plot

```{r shiny plot}
shinyApp(

  ui = fluidPage(
     # Application title
    titlePanel("Carbon Dioxide Uptake in Grass Plants"),
    helpText("Using R built in CO2 dataset, compares 3 plants, 
             in 2 locations, under 2 treatments."),

    # Sidebar with a slider input for number of bins
    sidebarLayout(
        sidebarPanel(

            selectInput("var", 
                        label = ("Select variable"),
                        choices = c("Plant",
                                    "Location",
                                    "Treatment"),
                        selected = "Plant"),
        ), #end side bar panel
        
    # Show a plot of the generated distribution
    
    mainPanel(plotlyOutput("boxplot"))
  )
), #end fluid page

  server = function(input, output) {
     output$boxplot <- renderPlotly({
      
      var <- switch(input$var,
                    "Plant" = CO2$Plant,
                    "Location" = CO2$Type,
                    "Treatment" = CO2$Treatment)
      
      plot_ly(CO2, x= ~uptake, color= var, type="box")
    })
  },

  options = list(height = 500)
)
```

